\documentclass[11pt,a4paper]{article}
\usepackage[margin=1.5cm]{geometry} % To control page layouts (margins, paper size, orientation).
\usepackage[hidelinks]{hyperref} % This makes the links clickable in the pdf and hides the ugly coloures boxes around links
\usepackage{enumitem} % Helps in controlling the style of lists
\setlist[itemize]{leftmargin=*, itemsep=2pt, topsep=2pt} % Removes extra indentation, reduces space between bullet points and also before/after the list.

\begin{document}
\begin{center}
    {\LARGE \textbf{Himmoy Gogoi}}\\
    \vspace{4pt}
    (biodata) \\
    \href{mailto:himmjezz16@gmail.com}{himmjezz16@gmail.com} \;|\;
    +91-9394541556 \;|\;
    \href{https://github.com/ryukiss}{github.com/Himmoy}\\
    North Lakhimpur, Assam
\end{center}

\vspace{8pt}
\noindent\\underline{textbf{Objective}}\\
2nd-year B.Tech Computer Science and Engineering student with a keen interest in programming and web development. Currently learning Data Structures in C++, Web Development, and eager to apply knowledge through projects, hackathons, and collaborative opportunities.

\vspace{8pt}
\noindent\underline{\textbf{Education}}\\
\textbf{B.Tech in Computer Science and Engineering}, NERIST, Arunachal Pradesh\hfill 2024 -- 2028 (expected)\\
Current Semester: 2nd Year, 1st Semester \\
Relevant Coursework: Programming in C/C++, Data Structures, Programming Tools \& Techniques

\vspace{8pt}
\noindent\underline{\textbf{Skills}}\\
\textbf{Programming:} C (basic), C++ (beginner), HTML \& CSS (beginner) \\
\textbf{Tools:} Overleaf (LaTeX), Git (beginner), Figma \\
\textbf{Concepts:} OOP (introductory), Problem Solving (learning stage), UI/UX (learning stage)

\vspace{8pt}
\noindent\underline{\textbf{Projects (Academic Practice)}}
\begin{itemize}
    \item \textbf{Console Calculator} -- C++ \\
    Built a basic calculator to perform arithmetic operations as part of programming practice.
    \item \textbf{Web Page} -- HTML, CSS \\
    Designed a simple tribute page to practice basic web development skills.
\end{itemize}

\vspace{8pt}
\noindent\underline{\textbf{Achievements}}
\begin{itemize}
    \item Successfully completed college coursework in C++ programming.
    \item Participated in coding workshops and technical events.
    \item Successfully completed FreeCodeCamp's \href{https://www.freecodecamp.org/certification/fcc-6a6c0306-18b6-448a-b067-86a66700f30c/responsive-web-design}{\textbf{Responsive Web 
    Design Certification}}
    \item Active in sports and cultural activities at the university.
\end{itemize}

\vspace{8pt}
\noindent\underline{\textbf{Extracurricular Activities}}
\begin{itemize}
    \item Learning fingerstyle guitar.
    \item Basketball (college intramural team).
    \item Reading and self-improvement.
\end{itemize}

\vspace{8pt}
\noindent\underline{\textbf{Languages}}
\begin{itemize}
    \item Tai Ahom (cultural)
    \item Assamese (native)
    \item English (fluent)
    \item Hindi (conversational)
    \item German (learning)
\end{itemize}

\vspace{8pt}
\noindent\underline{\textbf{Personal Details}}
\begin{itemize}
    \item Date of Birth: 10 September 2004
    \item Nationality: Indian
    \item Hobbies: Music, Basketball, Reading
\end{itemize}

\vspace{8pt}
\noindent\underline{\textbf{Declaration}}\\
I hereby declare that the information provided above is true to the best of my knowledge and belief.

\vspace{12pt}
\noindent Place: Assam \hfill Date: \today \\
Signature: Himmoy Gogoi

\end{document}
